Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-23 3dpas_intro.tex
v minor in abstract.
minor tweak in acknowledgement.

\section*{Acknowledgements}
This work was sponsored by NSF OCI-1059635 and made possible by the UK e-Science
Institute Research Theme on Dynamic Distributed Data-Intensive Programming
Abstractions and Systems. We thank Simon Dobson, Jon Weissman and Jon Blower for
useful initial discussions, as well as 3DPAS workshop attendees. Discussions of
the selected applications benefited from the generous help of Adam Barker, Jon
Blower, Julian Borrill, Silvia Delgado Olabarriaga, Steve Fisher, Keith Jackson,
Scott Klasky, Bob Mann, Don Middleton, Kees Nieuwenhuis, Manish Parashar,
Stephen Pascoe, and Jon Weissman, though any errors are the responsibility of
the authors.  Some of the work by Katz was supported by the National Science
Foundation while working at the Foundation; any opinion, finding, and
conclusions or recommendations expressed in this material are those of the
author(s) and do not necessarily reflect the views of the National Science
Foundation.

>>>>

\section*{Acknowledgements}
The workshop was sponsored by NSF OCI-1059635 and made possible by the UK
e-Science Institute Research Theme on Dynamic Distributed Data-Intensive
Programming Abstractions and Systems.  SJ contribution was also funded by NSF
CAREER ACI-1253644.  We thank Simon Dobson, Jon Weissman and Jon Blower for
useful initial discussions, as well as 3DPAS workshop attendees. Discussions of
the selected applications benefited from the generous help of Adam Barker, Jon
Blower, Julian Borrill, Silvia Delgado Olabarriaga, Steve Fisher, Keith Jackson,
Scott Klasky, Bob Mann, Don Middleton, Kees Nieuwenhuis, Manish Parashar,
Stephen Pascoe, and Jon Weissman, though any errors are the responsibility of
the authors.  Some of the work by Katz was supported by the National Science
Foundation while working at the Foundation; any opinion, finding, and
conclusions or recommendations expressed in this material are those of the
author(s) and do not necessarily reflect the views of the National Science
Foundation.
